Rank-based Training-Free NAS Algorithm

### 2024-02-28 paper/manuscript.tex

    \subsection{Search Algorithms}
    %%
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \begin{center}
            \begin{tabular}{ccc}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/naswot-acc.pdf}}}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ni-acc.pdf}}}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ninaswot-acc.pdf}}}
            \end{tabular}
            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NATS-Bench-TSS in the CIFAR-10 dataset 
            (b) NI score for 1,000 identical architectures from NATS-Bench-TSS in the CIFAR-10 dataset. 
            (c) NI score + NASWOT score for 1,000 identical architectures from NATS-Bench-TSS in the CIFAR-10 dataset.}
            \label{fig:ninaswot}
        \end{center}
        \vspace{-\baselineskip}
    \end{figure*}
    %%
    Several search algorithms have been applied to NAS, including random search, reinforcement learning, 
    and metaheuristic algorithms. 
    In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search (RS) is applied. 
    The advantage of RS is simple and easy to implement, and the result can be taken as a 
    baseline compared to more comprehensive search algorithms. Generally speaking, the performance of RS 
    is similar to other search algorithms when applying RS on a small search space, e.g., 
    NATS-Bench-TSS \cite{Dong_2021}. However, RS can no longer stand out in other search algorithms     
    when dealing with a relatively larger search space, e.g., NAS-Bench-101 \cite{ying2019nasbench101} 
    and NATS-Bench-SSS \cite{Dong_2021}.

@@

    We evaluate the performance of the proposed algorithm, \palg{}, 
    for searching the architectures of high accuracy. For comparison, several NAS 
    algorithms are included, e.g., random search (RS), regularized evolution algorithm 
    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{Williams:92}, 
    Bayesian optimization with hyper band (BOHB) \cite{falkner2018bohb}, RS with 
    weight sharing (RSWS) \cite{li2019random}, differentiable architecture search 
    with first order (DARTS-V1) \cite{liu2019darts}, DARTS with second order 
    (DARTS-V2) \cite{liu2019darts}, gradient-based search using differentiable 
    architecture sampler (GDAS) \cite{dong2019searching}, self-evaluated template 
    network (SETN) \cite{Dong_2019}, efficient NAS (ENAS) \cite{pham2018efficient}, 
    assisted REA (AREA) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
    %zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
    TE-NAS \cite{https://doi.org/10.48550/arxiv.2102.11535}, RS with NASWOT (RS-NASWOT) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
    RS with noise immunity (RS-NI) \cite{10092788}, RS with LogSynFlow (RS-LogSynFlow) \cite{Cavagnero_2023}, 
    and RS with ranking (RS-rank).

>>>>

    \subsection{Search Algorithms}
    %%
    \begin{figure*}[htb]
        \vspace{-\baselineskip}
        \begin{center}
            \begin{tabular}{ccc}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/naswot-acc.pdf}}}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ni-acc.pdf}}}
                \subfigure[]{\resizebox{0.33\textwidth}{!}{\includegraphics{asset/ninaswot-acc.pdf}}}
            \end{tabular}
            \caption{(a) NASWOT score for 1,000 randomly chosen architectures from NAS-Bench-201 in the CIFAR-10 dataset 
            (b) NI score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset. 
            (c) NI score + NASWOT score for 1,000 identical architectures from NAS-Bench-201 in the CIFAR-10 dataset.}
            \label{fig:ninaswot}
        \end{center}
        \vspace{-\baselineskip}
    \end{figure*}
    %%
    Several search algorithms have been applied to NAS, including random search, reinforcement learning, 
    and metaheuristic algorithms. 
    In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search (RS) is applied. 
    The advantage of RS is simple and easy to implement, and the result can be taken as a 
    baseline compared to more comprehensive search algorithms. Generally speaking, the performance of RS 
    is similar to other search algorithms when applying RS on a small search space, e.g., 
    NATS-Bench-TSS \cite{Dong_2021}. However, RS can no longer stand out in other search algorithms     
    when dealing with a relatively larger search space, e.g., NAS-Bench-101 \cite{ying2019nasbench101} 
    and NATS-Bench-SSS \cite{Dong_2021}.

@@

    We evaluate the performance of the proposed algorithm, \palg{}, 
    for searching the architectures of high accuracy. For comparison, several NAS 
    algorithms are included, e.g., random search (RS), regularized evolution algorithm 
    (REA) \cite{real2019regularized}, reinforcement learning (RL) \cite{williams1992simple}, 
    Bayesian optimization with hyper band (BOHB) \cite{falkner2018bohb}, RS with 
    weight sharing (RSWS) \cite{li2019random}, differentiable architecture search 
    with first order (DARTS-V1) \cite{liu2019darts}, DARTS with second order 
    (DARTS-V2) \cite{liu2019darts}, gradient-based search using differentiable 
    architecture sampler (GDAS) \cite{dong2019searching}, self-evaluated template 
    network (SETN) \cite{Dong_2019}, efficient NAS (ENAS) \cite{pham2018efficient}, 
    assisted REA (AREA) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
    %zero-cost NAS \cite{https://doi.org/10.48550/arxiv.2101.08134}, 
    TE-NAS \cite{https://doi.org/10.48550/arxiv.2102.11535}, RS with NASWOT (RS-NASWOT) \cite{https://doi.org/10.48550/arxiv.2006.04647}, 
    RS with noise immunity (RS-NI) \cite{10092788}, RS with LogSynFlow (RS-LogSynFlow) \cite{Cavagnero_2023}, 
    and RS with ranking (RS-rank).
